MP MetaAnalysis

### 2018-10-25 Paper_Analyses.Rmd
update 24.10.2018
better model interpretation
vocabulary summary
choosing figures to include

@@

@@

kable(pub_info, col.names = c("Publication Type", "# Items", "# Effect Sizes"))

@@

kable(comparison_info, col.names = c("Type of comparison", "# Papers", "# Effect Size"))
#table(db_ET_MP$es_method)
```

@@

#kable(es_info)
#table(dat$es_method, dat$short_cite)
# only missing from:
# Bailey & Plunkett (2002) <- crazy old data
# Renner (2017) <- just finished phd
#table(db_ET_MP$es_method)

#[KATIE] Can you also rename the factors here (like t_one)?
#[CHRISTINA] Mpt sire what you man, like in the table? You rename things later on, so why not.
#[KATIE] Actually, do we really need this table? When everything is summarized in the text, is that good enough?

@@

We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(dat, n_distinct(short_cite[es_method == "group_means_one" | es_method == "group_means_two"]))`) or using reported t-values (*n* = `r with(dat, n_distinct(short_cite[es_method == "t_one" | es_method == "t_two"]))`). Raw means and standard deviations were extracted from figures for `r with(dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers. In a within-participation design, when two means are compared (i.e. looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance based on t-values. Upon request we were provided with correlation values for one paper (Altvater-Mackensen, 2010); we were able to compute correlations using means, standard deviations, and t-values for *n* = `r with(corr_info, n_unique[imputed_corr == "no"]) - 1` (following Csibra, et al. 2016, Appendix B; see also Rabagliati, Ferguson, & Lew-Williams, 2018). Correlations were imputed for the remaining papers (see Black & Bergmann, 2017, for the same procedure). We could compute a total of `r sum(dat$is_mp == 0)` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)` for mispronunciations.

@@

[CHRISTINA: Do you think we have to revise this section? I think it's the same as in the proceedings paper.]
[KATIE: Are you concerned about the Publication Bias section in particular, or the Methods as a whole? In general, some of the Methods was written before the CogSci paper and in other places to flesh things out I rewrote what we had. Its definitely giving the same information and sometimes the wording is close, because there's not too many different ways to explain what a funnel plot is :)]

@@

[CHRISTINA: Let's both reread the full paper once it is ready and check that this is properly motivated and whether we do need to list them all. For now I think the last sentence is fine, but I would tend to prefer a reminder for the forgetful reader.]
[KATIE: that's reasonable! We had just listed everything 7 paragraphs before, which doesn't seem like a lot of "space".]

@@

[CHRISTINA: If we want to interpret here, how about the next bit.]
[KATIE: YES! This is an excellent point!!!]

@@

```{r FunnelCombo}

@@

```{r PcurveExport}

@@

[CHRISTINA: CAn you add the stats for the non-sig results?]
[KATIE: Are there stats that can be computed on the non-sig results? Or do you just want an n for significant and non-significant studies?]

@@

We first calculated the meta-analytic effect for object identification, i.e. looks to the target image in response to correctly pronounced words. The variance-weighted meta-analytic effect size Hedges' *g* was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`). This is a rather large effect size (according to the criteria set by Cohen, 1988; see also Bergmann, et al., 2018; for comparative meta-analytic effect sizes in language acquisition research). That the effect size is significantly above zero suggests that when presented with the correctly pronounced label, infants fixated the corresponding object. Our analysis of funnel plot asymmetry, however, found evidence for publication bias, which might lead to an overestimated effect sizes as smaller, non-significant results might not be published. Although the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)` suggests that this result is robust even when correcting for publication bias. In other words, we are confident that the true population mean lies above zero for object recognition of correctly pronounced words.

[CHRISTINA: Can you explain what the CI lower bound means here? I don't follow.]
[KATIE: What do you think about this? The CI lower bound stuff here actually comes from something you wrote, so tell me whether its correct.]

@@

We then calculated the meta-analytic effect for object identification in response to mispronounced words. In this case, the variance-weighted meta-analytic effect size Hedges' *g* was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was also significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`). This is considered a small effect size (Cohen, 1988), but significantly above zero, which suggests that even when presented with a mispronounced label, infants fixated the correct object. In other words, infants are able to resolve mispronunciations, a key skill in language processing We again note the publication bias (which was smaller in this condition), and the possibility that the effect size Hedges' *g* may be overestimated. But, as the p-curve indicated evidential value, we are confident in the overall patterns, namely that infants fixate the target even after hearing a mispronounced label.

@@

The above two analyses considered the data from mispronounced and correctly pronounced words separately. To evaluate mispronunciation sensitivity, we  compared the effect size Hedges' *g* for correct pronunciations with mispronunciations directly, merging the two datasets. The moderator test was significant, QM(`r r2(rma_MPeffect$m)`) = `r r2(rma_MPeffect$QM)`, *p* `r psig(rma_MPeffect$QMp)`.  Hedges' *g* for mispronunciation sensitivity was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`), which indicated that the responses across conditions were significantly different (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`). This confirms that although infants fixate the correct object for both correct pronunciations and mispronunciations, the observed fixations to target (as measured by the effect sizes) were significantly greater for correct pronunciations. In other words, we observe a significant difference between the two conditions and can now quantify the modulation of fixation behavior in terms of standardized effect sizes.

@@

To evaluate the different predictions we laid out in the introduction for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered, in days). In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not. Age did not significantly modulate object identification in response to correctly pronounced (QM(`r r2(rma_correct_age$m)`) = `r r2(rma_correct_age$QM)`, *p* `r psig(rma_correct_age$QMp)`) or mispronounced words (QM(`r r2(rma_MP_age$m)`) = `r r2(rma_MP_age$QM)`, *p* `r psig(rma_MP_age$QMp)`). The lack of a significant modulation together with the small estimates indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label. This relationship is plotted in Figure 2.

[CHRISTINA] CAN YOU ADD ESTIMATES AND THEIR CIS?? Ideally everywhere where you report a p-value
[KATIE: Do you know how to calculate Estimates and CIs for the Test of Moderators? Or do you mean reporting the estimates and CIs even when the moderator test is not significant?]

@@

We then examined the interaction between age and mispronunciation sensitivity (correct vs. mispronounced words) in our whole dataset. The moderator test was significant (QM(`r r2(rma_MPeffect_age$m)`) = `r r2(rma_MPeffect_age$QM)`, *p* `r psig(rma_MPeffect_age$QMp)`). This result is in line with the general observation that as infants mature they become better at language processing. The interaction between age and mispronunciation sensitivity, however, was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`), suggesting that as infants age, their mispronunciation sensitivity remains the same.

@@

Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers; production = `r with(vi1, papers[has_vocab == "production"])`) analyzed the relationship between vocabulary scores and mispronunciation sensitivity. There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment), so we analyze this data separately.

[KATIE] I DON'T KNOW HOW TO INTERPRET THESE RESULTS... THE FIXED EFFECTS MODEL ISN'T SIGNIFICANT FOR ANY OF THESE. IS THAT MEANINGFUL?
[CHRISTINA] SO WE DON'T WANT TO INTERPRET THE FIXED EFFECTS MODEL AT ALL, IT IS NOT SUITABLE BECAUSE THERE IS VARIANCE BETWEEN EVERY RECORD (LANGUAGE ETC).
I WOULD INTERPRET THE OVERALL CORRELATION AND THE CI, NOT THE P-VALUE (IN GENERAL). I ALSO WONDER WHETHER WE SHOULD MOVE THE SUBSET ANALYSES TO THE SUPPLEMENTARY MATERIALS AND JUST SAY OVERALL WE SEE NO RELATIONSHIPS AND CORRELATION COEFFICIENTS CONSISTENYL BELOW .1
WE THEREFORE MUST CONCLUDE THAT WITHIN NARROW AGE GROUPS VOCABULARY DOES NOT INFLUENCE ANYTHING WE LOOK AT. WE CANNOT DO THIS ANALYSIS FPOR MP SENSITIVITY BECAUSE WE DON'T HAVE THE NECESSARY RAW DATA.
[KATIE: Ah, so because for each paper the correlation and CI values straddle 0, this indicates that there really isn't much evidence for a relationship? I think it could make sense to add this to supplementary materials. Over the summer, I had also played around with looking at how collection of vocabulary data has dropped off over the years, even though more mispronunciation studies have been published. That might be something interesting to add. If we truly think that this is what is driving the development of mispronunciation sensitivity, then why are people not collecting this data?]
(BUT I WONDER WHETHER WECOULD ENCODE THE REPORTED INTERACTION TERMS AND THE CORRELATION AND THEN DO SOMETHING WITH THAT?)
[KATIE: I'm not really sure what you mean by this :(]

@@

metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
```

@@

metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
```

@@

metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
```

@@

metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
```

@@

The main goal of this paper was to assess mispronunciation sensitivity and its maturation with age. The results are clear: Although infants consider a mispronunciation as a better match with the target image than a distractor image, there was a consistent effect of mispronunciation sensitivity. This did not change with development. Of the 3 predictions and assumptions about the development of infants' sensitivity to mispronunciations discussed in the Introduction, the present results lend some support for the argument that mispronunciation sensitivity stays consistent as infants develop. This runs counter to existing theories of phono-lexical development, which predict either an increase (PRIMR ref) or decrease (Assim Model ref) in mispronunciation sensitivity.

[KATIE] CAN A CONCLUSION BE DRAWN FROM THE VOCABULARY RESULTS? IF SO, THIS IS THE PARAGRAPH

In sum, it seems that current theories of infants' phono-lexical development cannot fully capture our results and should be reconsidered with all the evidence in mind.

Alternatively, the lack of developmental change in mispronunciation sensitivity could be due to differences in the types of tasks given to infants of different ages. To examine this possibility, we include an exploratory analysis of whether different moderators and experimental design features were included at different ages, in addition to investigating the role that these moderators play in mispronunciation sensitivity.

@@

To understand the relationship between number of features changed and mispronunciation sensitivity, we  evaluated the effect size Hedges' *g* with number of features changed as a moderator. The moderator test was significant, QM(`r r2(rma_NFeatures$m)`) = `r r2(rma_NFeatures$QM)`, *p* `r psig(rma_NFeatures$QMp)`.  Hedges' *g* for number of features changed was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`), which indicated that as the number of features changed increased, the effect size Hedges' *g* significantly decreased (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`). We plot this relationship in Figure X. This confirms previous findings of a graded sensitivity to the number of features changed for both consonant (White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) mispronunciations as well as the importance of controlling for the degree of phonological mismatch in experimental design.

@@

p <- ggplot(dat_f, aes(Features_changed, g_calc, fill = Features_changed)) + 
  geom_boxplot() + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "none",
        axis.title.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")

@@

Although we did not have any specific predictions about the relationship between infant age and the impact of number of features changed on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship. When age was also included as a moderator, the moderator test was significant, QM(`r r2(rma_NFeatures$m)`) = `r r2(rma_NFeatures$QM)`, *p* `r psig(rma_NFeatures$QMp)`, but the interaction between age and number of features changed was not significant, $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`). This suggests that there is no relationship between infant age the impact of number of features changed on mispronunciation sensitivity.

@@

Although all papers included in the dataset also included correct pronunciations, not all papers included all three types of feature changes (i.e. 1-3). The age range for each type of number of features changed was `r with(nfeature_ages, min_age[n_feature == 1])` - `r with(nfeature_ages, max_age[n_feature == 1])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 1])`) for 1-feature mispronunciations, `r with(nfeature_ages, min_age[n_feature == 2])` - `r with(nfeature_ages, max_age[n_feature == 2])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 2])`) for 2-feature mispronunciations, and `r with(nfeature_ages, min_age[n_feature == 3])` - `r with(nfeature_ages, max_age[n_feature == 3])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 3])`) for 3-feature mispronunciations. Focusing on the ages where all three numbers of features changed were tested (i.e. `r with(nfeature_ages, min_age[n_feature == 3])` - `r with(nfeature_ages, max_age[n_feature == 3])` days), however, did not change the pattern of results.

@@

@@

sum_eff <- coef(summary(rma_Distractor))[4,]

@@

We next assessed whether distractor familiarity has an impact on the size of mispronunciation sensitivity. First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images that were paired with either a familiar or an unfamiliar distractor image. The moderator test was not significant QM(`r r2(rma_Distractor_MP$m)`) = `r r2(rma_Distractor_MP$QM)`, *p* `r psig(rma_Distractor_MP$QMp)`. This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the target image was paired with an image of a familiar or unfamiliar object. We next assessed whether distractor familiarity was related to mispronunciation sensitivity. We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator. The moderator test was significant, QM(`r r2(rma_Distractor$m)`) = `r r2(rma_Distractor$QM)`, *p* `r psig(rma_Distractor$QMp)`, but the interaction between distractor familiarity and condition was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`). These results suggest that overall, infants' familiarity with the distractor object (familiar or unfamiliar) did not impact their mispronunciation sensitivity.

@@

p <- ggplot(dat, aes(condition_label, g_calc, fill = condition_label)) + 
  geom_boxplot() + 
  facet_grid(.~dist_code) +
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")

  jpeg(filename = "figures/Figure_4Distractor_fam.jpg", 
       width = 500, height = 300, units = "px")

@@

  #[CHRISTINA] AGAIN, WHAT DO YOU THINK OF VIOLINS?

@@

object_pair_ages <- dat %>%
  group_by(object_pair) %>%
  summarize(min_age = r2(min(mean_age_1, na.rm=TRUE)),
            max_age = r2(max(mean_age_1, na.rm=TRUE)),
            mean_age = r2(mean(mean_age_1, na.rm=TRUE)))

@@

age_diff_dist <- t.xtable(t.test(fn$mean_age_1, ff$mean_age_1, paired = F))

@@

sum_eff <- round(coef(summary(rma_Distractor_MP))[2,], 2)

@@

>>>>

# wordcount()
# doesn't work...
# https://github.com/benmarwick/wordcountaddin

@@

g_SE <- function(x) paste0(r2(x$estimate), " (SE = ", r2(x$se), ")")

CI_p <- function(x) paste0("(95% CI[", r2(x$ci.lb), ", ", r2(x$ci.ub), "], *p* ", psig(x$pval), ")")

full_estimate <- function(x) paste0(" = ", r2(x$estimate), ", SE = ", r2(x$se), ", 95% CI[",  r2(x$ci.lb), ", ", r2(x$ci.ub),"], *p*", psig(x$pval))

# moderator test
mod_test <- function(x) paste0("QM(", r2(rma_MPeffect$m), ") = ", r2(rma_MPeffect$QM), ", *p*", psig(rma_MPeffect$QMp))

@@

#kable(pub_info, col.names = c("Publication Type", "# Items", "# Effect Sizes"))

@@

#kable(comparison_info, col.names = c("Type of comparison", "# Papers", "# Effect Size"))
#table(db_ET_MP$es_method)
```

@@

@@

We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(es_info, n_distinct(n_unique[es_method == "group_means_one" | es_method == "group_means_two"]))`) or using reported t-values (*n* = `r with(es_info, n_distinct(n_unique[es_method == "t_one" | es_method == "t_two"]))`). Raw means and standard deviations were extracted from figures for `r with(dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers. In a within-participation design, when two means are compared (i.e. looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance based on t-values. Upon request we were provided with correlation values for one paper (Altvater-Mackensen, 2010); we were able to compute correlations using means, standard deviations, and t-values for *n* = `r with(corr_info, n_unique[imputed_corr == "no"]) - 1` (following Csibra, et al. 2016, Appendix B; see also Rabagliati, Ferguson, & Lew-Williams, 2018). Correlations were imputed for the remaining papers (see Black & Bergmann, 2017, for the same procedure). We could compute a total of `r sum(dat$is_mp == 0)` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)` for mispronunciations.

@@

[CHRISTINA: Do you think we have to revise this section? I think it's the same as in the proceedings paper.]
[KATIE: Are you concerned about the Publication Bias section in particular, or the Methods as a whole? In general, some of the Methods was written before the CogSci paper and in other places to flesh things out I rewrote what we had in the CogSci paper. Its definitely giving the same information and sometimes the wording is close, because there's not too many different ways to explain what a funnel plot is :)]

@@

[CHRISTINA: Let's both reread the full paper once it is ready and check that this is properly motivated and whether we do need to list them all. For now I think the last sentence is fine, but I would tend to prefer a reminder for the forgetful reader.]
[KATIE: that's reasonable! We had just listed everything 7 paragraphs before, which doesn't seem like a lot of "space". Alternatively, this information could be listed in a table, and then just referred to.]

@@

@@

```{r FunnelCombo, echo = FALSE}

@@

```{r PcurveExport, echo = FALSE}

@@

@@

We first calculated the meta-analytic effect for object identification, i.e. looks to the target image in response to correctly pronounced words. The variance-weighted meta-analytic effect size Hedges' *g* was `r g_SE(sum_eff)` which was significantly different from zero `r CI_p(sum_eff)`. This is a rather large effect size (according to the criteria set by Cohen, 1988; see also Bergmann, et al., 2018; for comparative meta-analytic effect sizes in language acquisition research). That the effect size is significantly above zero suggests that when presented with the correctly pronounced label, infants fixated the corresponding object. Our analysis of funnel plot asymmetry, however, found evidence for publication bias, which might lead to an overestimated effect sizes as smaller, non-significant results might not be published. Although the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)` suggests that this result is robust even when correcting for publication bias. In other words, we are confident that the true population mean lies above zero for object recognition of correctly pronounced words.

[CHRISTINA: Can you explain what the CI lower bound means here? I don't follow.]
[KATIE: What do you think about this (last sentence)? The CI lower bound stuff here actually comes from something you wrote, so tell me whether its correct.]

@@

We then calculated the meta-analytic effect for object identification in response to mispronounced words. In this case, the variance-weighted meta-analytic effect size Hedges' *g* was `r g_SE(sum_eff)` which was also significantly different from zero `r CI_p(sum_eff)`. This is considered a small effect size (Cohen, 1988), but significantly above zero, which suggests that even when presented with a mispronounced label, infants fixated the correct object. In other words, infants are able to resolve mispronunciations, a key skill in language processing We again note the publication bias (which was smaller in this condition), and the possibility that the effect size Hedges' *g* may be overestimated. But, as the p-curve indicated evidential value, we are confident in the overall patterns, namely that infants fixate the target even after hearing a mispronounced label.

@@

The above two analyses considered the data from mispronounced and correctly pronounced words separately. To evaluate mispronunciation sensitivity, we  compared the effect size Hedges' *g* for correct pronunciations with mispronunciations directly, merging the two datasets. The moderator test was significant, `r mod_test(rma_MPeffect)`.  Hedges' *g* for mispronunciation sensitivity was `r g_SE(sum_eff)`, which indicated that the responses across conditions were significantly different `r CI_p(sum_eff)`. This confirms that although infants fixate the correct object for both correct pronunciations and mispronunciations, the observed fixations to target (as measured by the effect sizes) were significantly greater for correct pronunciations. In other words, we observe a significant difference between the two conditions and can now quantify the modulation of fixation behavior in terms of standardized effect sizes.

@@

To evaluate the different predictions we laid out in the introduction for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered, in days). In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not. Age did not significantly modulate object identification in response to correctly pronounced `r mod_test(rma_correct_age)` or mispronounce words `r mod_test(rma_MP_age)`. The lack of a significant modulation together with the small estimates indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label. This relationship is plotted in Figure 2.

@@

We then examined the interaction between age and mispronunciation sensitivity (correct vs. mispronounced words) in our whole dataset. The moderator test was significant `r mod_test(rma_MPeffect_age)`. This result is in line with the general observation that as infants mature they become better at language processing. The interaction between age and mispronunciation sensitivity, however, was not significant $\beta$`r full_estimate(sum_eff)`. The small estimate size, as well as inspection of Figure 2 suggests that as infants age, their mispronunciation sensitivity remains the same.

@@

Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers; production = `r with(vi1, papers[has_vocab == "production"])`) analyzed the relationship between vocabulary scores and mispronunciation sensitivity, specifically object recognition for correct pronunciations and mispronunciations. There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment), so we analyze this data separately.

[CHRISTINA] SO WE DON'T WANT TO INTERPRET THE FIXED EFFECTS MODEL AT ALL, IT IS NOT SUITABLE BECAUSE THERE IS VARIANCE BETWEEN EVERY RECORD (LANGUAGE ETC).
I WOULD INTERPRET THE OVERALL CORRELATION AND THE CI, NOT THE P-VALUE (IN GENERAL). I ALSO WONDER WHETHER WE SHOULD MOVE THE SUBSET ANALYSES TO THE SUPPLEMENTARY MATERIALS AND JUST SAY OVERALL WE SEE NO RELATIONSHIPS AND CORRELATION COEFFICIENTS CONSISTENYL BELOW .1
WE THEREFORE MUST CONCLUDE THAT WITHIN NARROW AGE GROUPS VOCABULARY DOES NOT INFLUENCE ANYTHING WE LOOK AT. WE CANNOT DO THIS ANALYSIS FPOR MP SENSITIVITY BECAUSE WE DON'T HAVE THE NECESSARY RAW DATA.
[KATIE: Ah, so because for each paper the correlation and CI values straddle 0, this indicates that there really isn't much evidence for a relationship? I've tried to write this out below, let me know what you think. Over the summer, I had also played around with looking at how collection of vocabulary data has dropped off over the years, even though more mispronunciation studies have been published. That might be something interesting to add. If we truly think that this is what is driving the development of mispronunciation sensitivity, then why are people not collecting this data?]
(BUT I WONDER WHETHER WECOULD ENCODE THE REPORTED INTERACTION TERMS AND THE CORRELATION AND THEN DO SOMETHING WITH THAT?)
[KATIE: I'm not really sure what you mean by this :(]

@@

CC <- metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")

# https://rdrr.io/cran/meta/man/forest.html
#forest(CC)

@@

CP <- metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")

[Katie: below, I'm using coweeta.uga.edu/publications/10436.pdf, page 80 as a model for writing up these results. I haven't the funniest clue what I'm doing! :p]

We first considered the relationship between vocabulary and object recognition for correct pronunciations. Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for 9 of 12 experimental conditions, with correlation values ranging from -0.17 to 0.48. The mean effect size XXX was 0.0897, but did not differ significantly from zero (95% CI[-0.0105; 0.1900] *p* = .0795). Higher production scores were also associated with greater object recognition in response to correct pronunciations for 9 of 16 experimental conditions, with correlation values ranging from -0.23 to 0.44. The mean effect size XXX was 0.0601, but did not differ significantly from zero (95% CI[-0.0331; 0.1533] *p* = .2061). For both comprehension and production scores, the small correlation effect sizes and large variances suggest a lack of relationship between vocabulary and object recognition for correct pronunciations.

@@

MC <- metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
```

@@

MP <- metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
```

We next considered the relationship between vocabulary and object recognition for mispronunciations. Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for 17 of 31 experimental conditions, with correlation values ranging from -0.35 to 0.57. The mean effect size XXX was 0.0377, but did not differ significantly from zero (95% CI[-0.0260; 0.1014] *p* = .2465). For production, however, lower production scores were associated with greater object recognition in response to mispronunciations for 16 of 31 experimental conditions, with correlation values ranging from -0.28 to 0.44. The mean effect size XXX was -0.0402, but did not differ significantly from zero (95% CI[-0.1043; 0.0238] *p* = .2181). For both comprehension and production scores, the small correlation effect sizes and large variances suggest a lack of relationship between vocabulary and object recognition for mispronunciations.

@@

The main goal of this paper was to assess mispronunciation sensitivity and its maturation with age. The results are clear: Although infants consider a mispronunciation as a better match with the target image than a distractor image, there was a consistent effect of mispronunciation sensitivity. This did not change with development. Of the 3 predictions and assumptions about the development of infants' sensitivity to mispronunciations discussed in the Introduction, the present results lend some support for the argument that mispronunciation sensitivity stays consistent as infants develop. This runs counter to existing theories of phono-lexical development, which predict either an increase (PRIMR ref) or decrease (Assim Model ref) in mispronunciation sensitivity. Furthermore, counter to the predictions for the PRIMR (PRIMR ref) and Assimilation(Assim ref) models, we found no relationship between vocabulary and target looking for correct pronunciations or mispronunciations. In sum, it seems that current theories of infants' phono-lexical development cannot fully capture our results and should be reconsidered with all the evidence in mind.

Alternatively, the lack of developmental change in mispronunciation sensitivity could be due to differences in the types of tasks given to infants of different ages. In the following section, we investigate the role that different moderators play in mispronunciation sensitivity. To investigate the possibility of systematic differences in the tasks across ages, we additionally include an exploratory analysis of whether different moderators and experimental design features were included at different ages.

@@

To understand the relationship between number of features changed and mispronunciation sensitivity, we  evaluated the effect size Hedges' *g* with number of features changed as a moderator. The moderator test was significant, `r mod_test(rma_NFeatures)`.  Hedges' *g* for number of features changed was `r g_SE(sum_eff)`, which indicated that as the number of features changed increased, the effect size Hedges' *g* significantly decreased `r CI_p(sum_eff)`. We plot this relationship in Figure 3. This confirms previous findings of a graded sensitivity to the number of features changed for both consonant (White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) mispronunciations as well as the importance of controlling for the degree of phonological mismatch in experimental design.

## Figure 3

@@

p <- ggplot(dat_f, aes(Features_changed, g_calc, fill = Features_changed)) + 
  geom_violin() + 
  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "none",
        axis.title.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")

@@

Although we did not have any specific predictions about the relationship between infant age and the impact of number of features changed on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship. When age was also included as a moderator, the moderator test was significant, `r mod_test(rma_NFeatures)`, but the interaction between age and number of features changed was not significant, $\beta$`r full_estimate(sum_eff)`. The small effect size for the interaction between age and number of features changed suggests that the impact of number of features changed on mispronunciation sensitivity does not change with infant age.

@@

Although all papers included in the dataset also included correct pronunciations, not all papers included all three types of feature changes (i.e. 1-3). The age range for each type of number of features changed was `r with(nfeature_ages, min_age[n_feature == 1])` - `r with(nfeature_ages, max_age[n_feature == 1])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 1])`) for 1-feature mispronunciations, `r with(nfeature_ages, min_age[n_feature == 2])` - `r with(nfeature_ages, max_age[n_feature == 2])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 2])`) for 2-feature mispronunciations, and `r with(nfeature_ages, min_age[n_feature == 3])` - `r with(nfeature_ages, max_age[n_feature == 3])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 3])`) for 3-feature mispronunciations. The reader should note that experimental conditions in which the number of features changed in a mispronunciation was not specified or the number of features changed was not consistent (e.g., one mispronunciation included a 2-feature change whereas another only a 1-feature change) are not included in these totals. An analysis focusing on the ages where all three numbers of features changed were tested (i.e. `r with(nfeature_ages, min_age[n_feature == 3])` - `r with(nfeature_ages, max_age[n_feature == 3])` days), however, did not change the pattern of results.

@@

misp_recog <- coef(summary(rma_Distractor_MP))[2,]

@@

misp_MS <- coef(summary(rma_Distractor))[4,]

@@

We next assessed whether distractor familiarity has an impact on the size of mispronunciation sensitivity. First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images that were paired with either a familiar or an unfamiliar distractor image. The moderator test was not significant `r mod_test(rma_Distractor_MP)` and the estimate for distractor familiarity was relatively small, $\beta$`r full_estimate(misp_recog)`. This suggests that upon hearing a mispronunciation, infants' looks to the target image were similar for when the target image was paired with an image of a familiar or unfamiliar object. We next assessed whether distractor familiarity was related to mispronunciation sensitivity. We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator. The moderator test was significant, `r mod_test(rma_Distractor)`, but the estimate for the interaction between distractor familiarity and condition was small and not significant $\beta$`r full_estimate(misp_MS)`. This relationship is plotted in Figure 4. The results suggest that overall, infants' familiarity with the distractor object (familiar or unfamiliar) did not impact their mispronunciation sensitivity.

## Figure 4

@@

p.DIST_ALL <- ggplot(dat, aes(condition_label, g_calc, fill = condition_label)) + 
  geom_violin() + 
  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  facet_grid(.~dist_code) +
  #labs(caption="a.") + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")

p.DIST_ALL

# lay <- rbind(c(1,1,2),
#       c(3,3,3))

  jpeg(filename = "figures/Figure_4_Distractor_Familiarity.jpg", 
       width = 500, height = 300, units = "px")

p.DIST_ALL

@@

@@

object_pair_ages <- dat %>%
  group_by(object_pair) %>%
  summarize(min_age = r2(min(mean_age_1, na.rm=TRUE)),
            max_age = r2(max(mean_age_1, na.rm=TRUE)),
            mean_age = r2(mean(mean_age_1, na.rm=TRUE)),
            sd_age = r2(sd(mean_age_1, na.rm=TRUE)))

@@

age_diff_dist <- t.test(fn$mean_age_1, ff$mean_age_1, paired = F)

@@

misp_MS_agesub <- round(coef(summary(rma_DistractorAge_agesub))[4,], 2)

@@

sum_eff2 <- coef(summary(rma_Location_MP))[2,]
